Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-01-05 RR_manuscript/Draft_RR.Rmd
update todos; remove trailing ws

SUM UP:
Neuroscience
Cognitive modeling
Clinical
Predictive models

@@

If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
<!-- TODO: mention speech domains -->
Given the continuous and transient nature of speech, identifying  speech parameters and temporal domain becomes a non-trivial task.
Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.

@@

<!-- TODO: include materials link and mailing lists -->
The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as "analysis teams".

@@

<!-- sample size info from Ecology RR -->
<!-- SC: rephrased and expanded -->
<!-- TODO: include citation to ECO RR -->
To identify the minimal sample size, we followed the method in [ECO RR].
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{team}}}$, see \Cref{s:meta-est}).
Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:

@@

<!-- TODO: ADD FORMULA of linear regression model -->
FORMULA

@@

<!-- TODO: DESCRIBE HOW WE WILL LOOK AT demographics -->

>>>>

<!-- TODO: SUMUP neuroscience, cognitive modeling, clinical, predictive models -->

@@

If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
Given the continuous and transient nature of speech, identifying speech parameters and temporal domains becomes a non-trivial task.
Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.

@@

<!-- TODO: add materials link and mailing lists -->
The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we refer to single researcher or small teams as "analysis teams".

@@

<!-- sample size info from Ecology RR -->
<!-- SC: rephrased and expanded -->
<!-- TODO: add citation to ECO RR -->
To identify the minimal sample size, we followed the method in [ECO RR].
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{team}}}$, see \Cref{s:meta-est}).
Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:

@@

<!-- TODO: ADD FORMULA of linear regression model to express majority of analysis -->
FORMULA

@@
